{Technical Documentation for TersectBrowser+}

### 2025-04-28 TechDoc/TechDoc.tex
Update TechDoc.tex
Added barcoding section

\title{
{\includegraphics[width=3cm, height=2.5cm]{TechDoc/Cran.jpg}}
\\
\includegraphics[width=7cm, height=1cm]{TechDoc/TB.jpg}
\\
{Technical Documentation for TersectBrowser+}
}

@@

\section{Overview}
This Technical Documentation describes the particular details of updating the original TersectBrowser developed by Tomasz Kurowski into the TersectBrowser+ by integrating multiple extension features.
\section{Architecture}
The TersectBrowser+ software is an Angular project, with an original frontend and backend written in Angular 8, and a separate extension space written in Angular 19 using Node 22. It was chosen to use a 'bolt-on' approach for the extensions in order to fit the project delivery within the time requirements, as well as allowing the new extensions to use up-to-date packages. The app is dockerized to allow both versions of node to be used seamlessly in different sections.

\section{Deployment}

@@

\section{TersectBrowser}
\section{TersectBrowser+}
\subsection{Variant Browser Extension}
\label{sec:Browser}
\subsubsection{Rationale}

@@

\begin{figure}[tbh]
\centering
\includegraphics[width=0.7\linewidth]{./image}
\caption{Architectural Design}
\label{fig:image}
\end{figure}

>>>>

\title{
%{\includegraphics[width=3cm, height=2.5cm]{TechDoc/Cran.jpg}}
%\\
%\includegraphics[width=7cm, height=1cm]{TechDoc/TB.jpg}
%\\
{Technical Documentation for TersectBrowser+}
}

@@

\section{Overview}
This Technical Documentation describes the particular details of updating the original TersectBrowser developed by Tomasz Kurowski into the TersectBrowser+ by integrating multiple extension features.

\section{Architecture}
The TersectBrowser+ software is an Angular project, with an original frontend and backend written in Angular 8, and a separate extension space written in Angular 19 using Node 22. It was chosen to use a 'bolt-on' approach for the extensions in order to fit the project delivery within the time requirements, as well as allowing the new extensions to use up-to-date packages. The app is dockerized to allow both versions of node to be used seamlessly in different sections.

For the TersectBrowser+ update to the original TersectBrowser, main changes have been made to the frontend implementation of features added in a separate extension section of the project. The main addition is in a 'genome-browser' extension, which contains elements for each of the specific features mentioned in the project brief.

\section{Deployment}
The GitHub project \url{https://github.com/Tersect-Browser/Tersect-browser} README provides detailed instructions for setup, dependencies, and deployment, however the main outline is given here.

@@

The main requirements for TersectBrowser+ deployment are:
\begin{itemize}
    \item nvm (versions 16 and 22 specifically, as these will be deployed separately)
    \item npm registery \url{https://registry.npmjs.org/}
    \item Angular CLI v1.7.1
    \item Tersect CLI
    \item JBrowse CLI
    \item MongoDB
    \item Python virtual environment
    \item RapidNJ / Rosetta
\end{itemize}

\section{TersectBrowser+}
\subsection{Variant Browser Extension}
\label{sec:Browser}
\subsubsection{Rationale}

@@
